### 2016-01-21 math_modeling/hw/hw1/result.tex
math modeling
finished modeling

\newpage
\item The following table gives the depth $Z$ of water in feet for surface points with rectangular
coordinates $X, Y$ in meters. The depth of measurements were made at low tide. Your ship has a draft of 5
feet. What region should you avoid within the rectangle $[75, 200] \times [−50, 150]$?
\begin{center}
\begin{tabular}{c | c | c}
X & Y & Z\\
\hline
129.0 & 7.5 & 4\\
140.0 & 141.5 & 8\\
108.5 & 28.0 & 6\\
88.0 & 147.0 & 8\\
185.5 & 22.5 & 6\\
195.0 & 137.5 & 8\\
105.5 & 85.5 & 8\\
157.5 & -6.5 & 9\\
107.5 & -81.0 & 9\\
77.0 & 3.0 & 8\\
162.0 & -66.5 & 9\\
162.0 & 84.0 & 4\\
117.5 & -38.5 & 9
\end{tabular}
\end{center}

>>>>

\newpage
%% data <- Read.table('myfile.txt')
%% lm(data[,2]~data[,2]+data[,1]) will return equation of lakebed plane
%% Use Mathematica to predict where the depth is less than 5 on lakebed plane
%% The equation needs to be such that plane.z < 5
\item The following table gives the depth $Z$ of water in feet for surface points with rectangular
coordinates $X, Y$ in meters. The depth of measurements were made at low tide. Your ship has a draft of 5
feet. What region should you avoid within the rectangle $[75, 200] \times [-50, 150]$?
\begin{center}
\begin{tabular}{c | c | c}
X & Y & Z\\
\hline
129.0 & 7.5 & 4\\
140.0 & 141.5 & 8\\
108.5 & 28.0 & 6\\
88.0 & 147.0 & 8\\
185.5 & 22.5 & 6\\
195.0 & 137.5 & 8\\
105.5 & 85.5 & 8\\
157.5 & -6.5 & 9\\
107.5 & -81.0 & 9\\
77.0 & 3.0 & 8\\
162.0 & -66.5 & 9\\
162.0 & 84.0 & 4\\
117.5 & -38.5 & 9
\end{tabular}
\end{center}

\inputminted{r}{lakebedr.R}
\includegraphics[scale=0.7]{three_plot}
\noindent\\
The entire area appears to be safe. However, the plane is the result of a best fit, so the corner
of the lakebed should be avoided just to be sure.
